---
title: "quarto_ex"
format: html
editor: visual
---

# Load Packages

## Reproducible/Shareable Package Loading - `librarian` Package
```{r}

if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

# librarian downloads, if not already downloaded, and reads in needed packages
librarian::shelf(tidyverse, here, janitor, RPostgres, DBI)


```

## Semi-Shareable Package Loading
```{r}

library(tidyverse)
library(here)
library(janitor)
library(janitor)
library(janitor)
library(RPostgres)
library(DBI)

```

# Loading Data

## Reproducible File Paths - Relative File Path: `here` Package

### Make `data` Folder, Connect to DB, Query Data, Save Data for offline use
```{r}

# Make Data Folder
if (!dir.exists("data")){
  dir.create(here("data"))
}

# DB Connection 
ribbitr_connection <- dbConnect(drv = dbDriver("Postgres"),
                                host = Sys.getenv("aws_host"),
                                port = Sys.getenv("aws_port"),
                                dbname = Sys.getenv("aws_dbname"),
                                user = Sys.getenv("aws_user"),
                                password = Sys.getenv("aws_password"))

# Set search_path to `survey_data` schema
dbExecute(ribbitr_connection, "set search_path = 'survey_data'")

# SQL query
sql <- "select l.location, r.region, s.site, v.date, v.survey_time, s2.duration_minutes, 
        c.species_capture, c.svl_mm
        from location l
        join region r on l.location_id = r.location_id
        join site s on r.region_id = s.region_id
        join visit v on s.site_id = v.site_id
        join survey s2 on v.visit_id = s2.visit_id
        join capture c on s2.survey_id = c.survey_id"

# Send Query to DB
clean_data <- dbGetQuery(ribbitr_connection, sql)

# Save Data for offline use
write_csv(clean_data, here("data", "clean_data.csv"))

rm(clean_data)
```

### Load Data Offline
```{r}

clean_data <- read_csv(here("data", "clean_data.csv"))

```


## Non-Reproducible File Paths - Direct File Paths

### Load Data Offline - Sends `clean_data.csv` Through Email
```{r}

# Set working directory
setwd("/Users/JaketheBoss/Documents/RIBBiTR/reproducible_script")

# Throw Error due to no "data" folder or csv in a different location
clean_data <- read_csv("data/clean_data.csv")

# Or Direct File Path
clean_data <- read_csv("/Users/JaketheBoss/Documents/RIBBiTR/reproducible_script/data/clean_data.csv")

```

